Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-17 report/report.tex
Update todo
Fix remaining references

% Writing:
% TODO: Write introduction section
% TODO: Write Collision study implementation section
    % TODO: Edge distance algorithm, algorithm

% Pictures
% Introduction
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
% Collision study implementation
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, picture

% Scietific study
    % TODO: Find papers and topics for the scientific study (Building footprints, building heights, LOD levels, road rendering, terrain (Procedural roads))
    % TODO: Scientific study, disposition

@@

\bibitem{biljecki-16}
%TODO
Biljecki, F
2016
THE MOST COMMON GEOMETRIC AND SEMANTIC ERRORS IN CITYGML DATASETS

@@

\bibitem{stojanovski-19}
%TODO
Stojanovski, T.
2019
Typo-morphology of transportation - Looking at historical development and multimodal futures of Swedish streets and roads

@@

\bibitem{vanegas-10}
%TODO
Vanegas, C.
2010
Modelling the Appearance and Behaviour of Urban Spaces

>>>>

% Sunday
% Pictures
% Introduction
    % TODO: Figure showing the unique characteristics of footpaths vs other road types (OSM Screeshot)
    % TODO: Virtual city picture
% Scietific study
    % TODO: Find papers and topics for the scientific study (building heights, road rendering, terrain (Procedural roads))
    % TODO: Scientific study, disposition
% TODO: Edge distance algorithm, algorithm

% Monday
% TODO: Write introduction section
% TODO: Write Collision study implementation section
% TODO: Write Scientific study
% Collision study implementation
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, picture

@@

\bibitem{biljecki-16}
Biljecki, F., Ledoux, H., Du, X., Stoter, J., Soon, K., and Khoo, V. (2016). The most common geometric and semantic errors in CityGML datasets. 10.5194/isprs-annals-IV-2-W1-13-2016.

@@

\bibitem{stojanovski-19}
Stojanovski, T. (2019). Typo-morphology of transportation -Looking at historical development and multimodal futures of Swedish streets and roads. Conference paper. ISUF 2019 – ХХVI International Seminar on Urban Form 2019, At Nicosia, Cyprus

@@

\bibitem{vanegas-10}
Vanegas, C., Aliaga, D., Mueller, P., Waddell, P., Watson, B. and Wonka, P. (2010). Modeling the Appearance and Behavior of Urban Spaces. Computer Graphics Forum. 29. 25-42. 10.1111/j.1467-8659.2009.01535.x.
